---
title: "Visualizations"
subtitle: "32 Visualizations"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number-section: false
    highlight: tango
editor_options: 
  chunk_output_type: console
---

```{r setup, echo = F}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

```{r}
library(here)
library(tidyverse)
library(metafor)
library(ggrepel)
library(ggdist)
library(distributional)
library(kableExtra)
library(ggtext)

# Read data created in generate_MA_data.R
viz_MA_data <- readRDS(here("exp3_vote_counting", "data", "exp3_ma_data.RDS"))

# Source files for creating each visualization type
source(here("exp3_vote_counting", "viz_MARC_exp3.R"))
```

### Summary of Meta-Analytic Data by Level of Factor B

+ We generated 100,000 meta-analytic datasets with $k = 10$ studies (according to the model specified in project narrative, assumes $\delta = 0.15$). 
+ Of those 100,000, we filtered to keep only the ones that had the desired number of negative effects for factor A (0, 1, 3, 6) and those that have a summary effect that rounds to delta = 0.15. This results in 2,456 meta-analytic datasets. 
+ We plotted each of the 2,456 datasets (using the Full MARC plot version), and chose 1 meta-analytic dataset per level of factor A that represented a "typical" distribution of effect sizes among all plots with the given number of negative effects.
+ The 4 meta-analytic datasets chosen had the following IDs: 

| ma_id | A |
|--------| --|
| 1796 | 0 negative effects |
| 377 | 1 negative effect |
| 104 | 3 negative effects |
| 31284 | 6 negative effects| 

+ Each of the 4 meta-analytic datasets chosen for Factor A are re-weighted to achieve each of the 4 levels of Factor B. Therefore, there are a total of 16 meta-analytic datasets used to represent the 16 A x B experimental conditions.
+ The following table shows the meta-analytic summary info for the 16 datasets used in this experiment:

```{r}
summary_data <- viz_MA_data |>
  filter(ma_id %in% c(1796, 377, 104, 31284)) |>
  group_by(B, ma_id, sig_level, neg_count) |>
  summarize(
    es = weighted.mean(d_j, w_j_rescaled),
    W = sum(w_j_rescaled),
    se = sqrt(1 / sum(w_j_rescaled))
  ) |>
  mutate(prob_pos = pnorm(0, es, se, lower.tail = FALSE))

conditions <- summary_data |>
  group_by(B) |>
  summarize(
    avg_es = mean(es),
    avg_W = mean(W),
    avg_se = mean(se),
    avg_prob = mean(prob_pos)
  )

conditions |>
  kable() |>
  kable_minimal()
```

+ **B** = 4 levels of Factor B.
+ **avg_es** = average meta-analytic summary effect size for this experimental condition.
+ **avg_W** = average sum of weights for this experimental condition.
+ **avg_se** = average standard error of the summary effect for this experimental condition.
+ **avg_prob** = average $P(\hat{\delta} > 0)$ for the corresponding summary effect & SE specified by this experimental condition.

Below we show an example visualization for each of the 16 experimental conditions.

# B = 1 (`r round(conditions$avg_prob[1],3)` prob $\delta$>0)

```{r}
######################## B = 1 ############################
B1_data <- viz_MA_data %>%
  filter(B == 1)
```

#### Factor A1: 0 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B1_data |>
  filter(neg_count == 0, ma_id == 1796) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A0_b1_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A0_b1_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

#### Factor A2: 1 negative effect
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B1_data |>
  filter(neg_count == 1, ma_id == 377) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A1_b1_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A1_b1_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

#### Factor A3: 3 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B1_data |>
  filter(neg_count == 3, ma_id == 104) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A3_b1_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),

  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A3_b1_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

```{r, echo = FALSE, eval = FALSE}
# is this needed?

library(metaviz)
viz_forest(
  x = data.frame(d_j = data$d_j, se_j = data$se_j_rescaled),
  study_labels = c(1:10),
  group = c(1, 1, 2, 1, 3, 1, 2, 3, 3, 1)
)
```


#### Factor A4: 6 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B1_data |>
  filter(neg_count == 6, ma_id == 31284) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A6_b1_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r, eval = FALSE, echo = FALSE}
# is this needed?

library(metaviz)
x <- data |> select(d = d_j, se = se_j)
viz_forest(x)

viz_forest(d = data$d_j, se = data$se_j)
viz_forest(data$d_j, data$se_j)
viz_forest(x = data$d_j, se = data$se_j)

x <- data |>
  transmute(d = d_j, se = se_j) |>
  as.data.frame()

viz_forest(x) +
  labs(x = "SMD")
```


```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A6_b1_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

# B = 2 (`r round(conditions$avg_prob[2],3)` prob $\delta$>0)

```{r}
######################## B = 2 ############################
B2_data <- viz_MA_data %>%
  filter(B == 2)
```

#### Factor A1: 0 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B2_data |>
  filter(neg_count == 0, ma_id == 1796) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A0_b2_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A0_b2_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

#### Factor A2: 1 negative effect
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B2_data |>
  filter(neg_count == 1, ma_id == 377) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A1_b2_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A1_b2_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

#### Factor A3: 3 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B2_data |>
  filter(neg_count == 3, ma_id == 104) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A3_b2_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A3_b2_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

#### Factor A4: 6 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B2_data |>
  filter(neg_count == 6, ma_id == 31284) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A6_b2_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A6_b2_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

# B = 3 (`r round(conditions$avg_prob[3],3)` prob $\delta$>0)

```{r}
######################## B = 3 ############################
B3_data <- viz_MA_data %>%
  filter(B == 3)
```

#### Factor A1: 0 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B3_data |>
  filter(neg_count == 0, ma_id == 1796) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A0_b3_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A0_b3_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

#### Factor A2: 1 negative effect
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B3_data |>
  filter(neg_count == 1, ma_id == 377) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A1_b3_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A1_b3_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

#### Factor A3: 3 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B3_data |>
  filter(neg_count == 3, ma_id == 104) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A3_b3_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A3_b3_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

#### Factor A4: 6 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B3_data |>
  filter(neg_count == 6, ma_id == 31284) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A6_b3_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A6_b3_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

# B = 4 (`r round(conditions$avg_prob[4],3)` prob $\delta$>0)

```{r}
######################## B = 4 ############################
B4_data <- viz_MA_data %>%
  filter(B == 4)
```

#### Factor A1: 0 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B4_data |>
  filter(neg_count == 0, ma_id == 1796) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A0_b4_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A0_b4_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

#### Factor A2: 1 negative effect
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B4_data |>
  filter(neg_count == 1, ma_id == 377) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A1_b4_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A1_b4_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

#### Factor A3: 3 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B4_data |>
  filter(neg_count == 3, ma_id == 104) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A3_b4_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A3_b4_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```

#### Factor A4: 6 negative effects
```{r}
#| fig.width: 7.5
#| fig.height: 5
data <- B4_data |>
  filter(neg_count == 6, ma_id == 31284) |>
  slice(1:10)

viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A6_b4_F.png"),
  width = 7.5,
  height = 5,
  dpi = 700
)
```

```{r}
#| fig.width: 7.5
#| fig.height: 3.2
viz_MARC_exp3(
  d_j = data$d_j,
  se_j = data$se_j_rescaled,
  summary_only = TRUE,
  study_labels = c(1:10),
  seed = 2427,
  y_limits_rect = c(0.78, 1.22),
  x_limits = c(-1, 1),
  font_sizes = c(10, 8, 6, 8, 8, 7, 10),
  max_dot_size = 5
)

ggsave(
  here("exp3_vote_counting", "images", "A6_b4_S.png"),
  width = 7.5,
  height = 3.2,
  dpi = 700
)
```